Convolutional equivalent layer for gravity data processing

### 2020-04-06 manuscript/figures.tex
include parameter values used to compute the continuation

\plot{Figure10_r1}{width=6cm}{
	{Application to synthetic data.
	(a) Gravity data produced by the synthetic sources at $z = -XXXX$ m.
	(b) Residuals between the simulated data shown in a and the upward-continued 
	gravity data obtained with the fast equivalent-layer technique (not shown), with 
	mean $XXXXXX$ mGal and standard deviation $XXXXXX$ mGal. 
	(c) Residuals between the simulated data shown in a and the upward-continued 
	gravity data obtained with our method (not shown), with mean $XXXXX$ mGal and 
	standard deviation $XXXXX$ mGal. 
	The total computation times spent by the fast equivalent-layer technique and 
	our method were $7.62026$ and $0.00834$ seconds, respectively.}
	\label{fig:upward_comparison}
}

\plot{Figure11_r1}{width=6cm}{
	{Application to synthetic data. 
	(a) Gravity data produced by the synthetic sources at $z = -XXXX$ m.
	(b) Residuals between the simulated data shown in a and the downward-continued 
	gravity data obtained with the fast equivalent-layer technique (not shown), with 
	mean $XXXXXX$ mGal and standard deviation $XXXXXX$ mGal. 
	(c) Residuals between the simulated data shown in a and the downward-continued 
	gravity data obtained with our method (not shown), with mean $XXXXX$ mGal and 
	standard deviation $XXXXX$ mGal. 
	The total computation times spent by the fast equivalent-layer technique and 
	our method were $7.59654$ and $0.00547$ seconds, respectively.}
	\label{fig:downward_comparison}
}

>>>>

\plot{Figure10_r1}{width=6cm}{
	{Application to synthetic data.
	(a) Gravity data produced by the synthetic sources at $z = -300$ m.
	(b) Residuals between the simulated data shown in a and the upward-continued 
	gravity data obtained with the fast equivalent-layer technique (not shown), with 
	mean $-0.0003$ mGal and standard deviation $0.0124$ mGal. 
	(c) Residuals between the simulated data shown in a and the upward-continued 
	gravity data obtained with our method (not shown), with mean $-0.0003$ mGal and 
	standard deviation $0.0124$ mGal. 
	The total computation times spent by the fast equivalent-layer technique and 
	our method were $7.62026$ and $0.00834$ seconds, respectively.}
	\label{fig:upward_comparison}
}

\plot{Figure11_r1}{width=6cm}{
	{Application to synthetic data. 
	(a) Gravity data produced by the synthetic sources at $z = -50$ m.
	(b) Residuals between the simulated data shown in a and the downward-continued 
	gravity data obtained with the fast equivalent-layer technique (not shown), with 
	mean $0.0001$ mGal and standard deviation $0.0079$ mGal. 
	(c) Residuals between the simulated data shown in a and the downward-continued 
	gravity data obtained with our method (not shown), with mean $0.0001$ mGal and 
	standard deviation $0.0079$ mGal. 
	The total computation times spent by the fast equivalent-layer technique and 
	our method were $7.59654$ and $0.00547$ seconds, respectively.}
	\label{fig:downward_comparison}
}
